\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2020-04-01 gwnnDraft02.tex
changes
second ref edits

The form of the GW energy density at the time of nucleation is given by~\citep{Breitbach:2018ddu},
\begin{equation}\label{eqn::GWengdensity}
h^2\Omega_{\textrm{GW}}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
\end{equation}
where we use $v \sim 1$ for runaway bubbles. Quantities such as $\Omega_{\textrm{GW}}^*$ that are calculated at the time of nucleation are denoted with an asterisk, and they must then be evolved to relate to their values at the time of observation.  $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions:
\begin{equation}\label{eqn::spectralshape}
S(f) = \frac{3.8 \,(f/f_p)^{2.8}}{1 + 2.8\,(f/f_p)^{3.8}}.
\end{equation}
The peak frequency, $f_{p}$ is a function of the temperature of the SM at the time of nucleation.  The various hidden sectors can phase transition at different scales and therefore temperatures, causing a shift in the GW spectrum's peak frequency given by~\cite{Huber_2008},
%
\begin{equation}\label{eqn:peakFrequency}
f_{p} = 3.8 \times 10^{-8} \, \textrm{Hz}\, \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}},
\end{equation}
%
where $g_*$  is calculated using Eq.~(\ref{eqn:RelaDOF}), although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant.

@@

\begin{equation}
\begin{split}
h^2\Omega_{v}^* = 1.6 \times 10^{-1} \, v  \, \bigg( \frac{\kappa_{v}\;  \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^1  S_{v}(f),
\\
h^2\Omega_{turb}^* = 2.01\times 10^{1} \, v \, \bigg( \frac{\kappa_{turb} \; \alpha}{1 + \alpha} \bigg)^{3/2} \bigg( \frac{H}{\beta} \bigg)^1  S_{turb}(f).
\end{split}
\end{equation}
Unlike the runaway case, we do not assume $v = 1$ due to the bubbles reaching a terminal velocity. The MHD efficiency factor is a fraction of the sound waves, $\kappa_{turb} = \epsilon\kappa_{v}$. Current simulations have motivated a range of $\epsilon \sim 0.05 - 0.10$  \citep{Caprini:2015zlo}, where we take the optimistic case of $\epsilon = 0.10$. Both contributions have unique spectral shapes, given to be \citep{Breitbach:2018ddu}, 
%
\begin{equation}
\begin{split}
S_{v}(f) = (f/f_{p,v})^3\bigg(\frac{7}{4+3(f/f_{p,v})^2}\bigg)^{7/2},
\\
S_{turb}(f) = \frac{(f/f_{p,turb})^{3}}{(1 + f/f_{p,turb})^{11/3} (1 + 8\pi(f/H))}.
\end{split}
\end{equation}
The MHD energy density has a spectral shape dependent on the Hubble rate at the time of nucleation, $H$.  Similar to the scalar spectral shape in Eq.~(\ref{eqn::spectralshape}), the frequencies are scaled by their respective temperature dependent peak frequency,

>>>>

The form of the GW energy density at the time of nucleation is given by~\citep{Breitbach:2018ddu},
\begin{equation}\label{eqn::GWengdensity}
h^2\Omega_{\textrm{GW}}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
\end{equation}
where we use $v = 1$ for runaway bubbles. Quantities such as $\Omega_{\textrm{GW}}^*$ that are calculated at the time of nucleation are denoted with an asterisk, and they must then be evolved to relate to their values at the time of observation.  $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions:
\begin{equation}\label{eqn::spectralshape}
S(f) = \frac{3.8 \,(f/f_p)^{2.8}}{1 + 2.8\,(f/f_p)^{3.8}}.
\end{equation}
The peak frequency, $f_{p}$ is a function of the temperature of the SM at the time of nucleation.  The various hidden sectors can phase transition at different scales and therefore temperatures, causing a shift in the GW spectrum's peak frequency given by~\cite{Huber_2008},
%
\begin{equation}\label{eqn:peakFrequency}
f_{p} = 3.8 \times 10^{-8} \, \textrm{Hz}\, \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}},
\end{equation}
%
where $g_*$  is calculated using Eq.~(\ref{eqn:RelaDOF}), although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant.

@@

\begin{equation}\label{eqn::SWMHD}
\begin{split}
h^2\Omega_{v}^* = 1.6 \times 10^{-1} \, v  \, \bigg( \frac{\kappa_{v}\;  \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^1  S_{v}(f),
\\
h^2\Omega_{turb}^* = 2.01\times 10^{1} \, v \, \bigg( \frac{\kappa_{turb} \; \alpha}{1 + \alpha} \bigg)^{3/2} \bigg( \frac{H}{\beta} \bigg)^1  S_{turb}(f).
\end{split}
\end{equation}
Unlike the runaway case, we do not assume $v = 1$ due to the bubbles reaching a terminal velocity. The MHD efficiency factor is a fraction of the sound waves, $\kappa_{turb} = \epsilon\kappa_{v}$. Current simulations have motivated a range of $\epsilon \sim 0.05 - 0.10$  \citep{Caprini:2015zlo}, where we take the optimistic case of $\epsilon = 0.10$. Both contributions have unique spectral shapes, given to be \citep{Breitbach:2018ddu},

In the sound wave case, these parametizations are extracted from simulations with $\beta/H < 100$ corresponding to a long lasting sound wave component. For high $\beta/H$ the transition timescale from sound wave to MHD turbulence is much shorter than the Hubble time. When casting the model expectations for $\beta/H = 10^4$ we enter a regime at which ~(\ref{eqn::SNR}) may be overestimated the sound wave contribution. Investigations of this regime have been done in \citep{Hindmarsh:2017gnf, Ellis:2018mja, Ellis_2019}. Although Independent of overestimating or signal, this paper focuses on the unique spectral shapes that are formed in these extraneous models. Therefore we project our results for high $\beta/H$ in Fig.~\ref{fig:Haasw}  to motivate the spectral profiles and not detectability.
%
\begin{equation}
\begin{split}
S_{v}(f) = (f/f_{p,v})^3\bigg(\frac{7}{4+3(f/f_{p,v})^2}\bigg)^{7/2},
\\
S_{turb}(f) = \frac{(f/f_{p,turb})^{3}}{(1 + f/f_{p,turb})^{11/3} (1 + 8\pi(f/H))}.
\end{split}
\end{equation}
The MHD energy density has a spectral shape dependent on the Hubble rate at the time of nucleation, $H$.  Similar to the scalar spectral shape in Eq.~(\ref{eqn::spectralshape}), the frequencies are scaled by their respective temperature dependent peak frequency,
